A Low-Effort Analytics Platform for Visualizing Evolving Flask-Based Python Web Services

### 2018-01-23 paper.tex
renamed and moved to IEEE style

\documentclass{sig-alternate-05-2015}
	\pdfpagewidth=8.5truein
	\pdfpageheight=11truein

@@

\CopyrightYear{2018}
\setcopyright{acmcopyright}
\conferenceinfo{SAC 2018,}{April 09-13, 2018, Pau, France}
%\isbn{978-1-4503-5191-1/18/04}\acmPrice{\$15.00}
%\doi{DOI: http://dx.doi.org/xxx}

@@

\numberofauthors{4}
\author{
\alignauthor Patrick Vogel\\
\email{p.p.vogel@student.rug.nl}
%
\alignauthor Thijs Klooster\\
\email{t.klooster.1@student.rug.nl}
%
\and
\alignauthor Vasilios Andrikopoulos\\
\email{v.andrikopoulos@rug.nl}
%
\alignauthor Mircea Lungu\\
\email{m.f.lungu@rug.nl}
%
\sharedaffiliation
\affaddr{Johann Bernoulli Institute for Mathematics and Computer Science}\\
\affaddr{University of Groningen, the Netherlands}\\
}
\date{\today}

@@

\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10010520.10010553.10010554</concept_id>
	<concept_desc>Computer systems organization~Robotics</concept_desc>
	<concept_significance>100</concept_significance>
	</concept>
	<concept>
	<concept_id>10003033.10003083.10003095</concept_id>
	<concept_desc>Networks~Network reliability</concept_desc>
	<concept_significance>100</concept_significance>
	</concept>
	</ccs2012>  
\end{CCSXML}

\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

>>>>

\documentclass[conference]{IEEEtran}
	\pdfpagewidth=8.5truein
	\pdfpageheight=11truein

@@

@@

\author{
\IEEEauthorblockN{Patrick Vogel, Thijs Klooster, Vasilios Andrikopoulos, Mircea Lungu}\\
Johann Bernoulli Institute for Mathematics and Computer Science\\
University of Groningen, Netherland\\
Email: \{t.klooster.1,p.p.vogel\}@student.rug.nl, \{v.andrikopoulos,m.f.lungu\}@rug.nl 
}

@@
